### 2014-06-11 ApTranscriptome_TR.Rmd

# Load Bioconductor libraries
#source("http://bioconductor.org/biocLite.R")
#biocLite("topGO")
#biocLite("Rgraphviz")
#biocLite("RDAVIDWebService")
#biocLite("GOSemSim")
library(topGO) 
library(Rgraphviz)
library(GOSemSim)

@@

```{r responsive_transcripts}
interaction.lms <- RxNlmAIC[which(Map(grepFunc, RxNlmAIC, term = "colonyAr:") == TRUE)]
other.lms <- RxNlmAIC[setdiff(names(RxNlmAIC), names(interaction.lms))]
temperature.lms <- other.lms[which(Map(grepFunc, other.lms, term = "val") == TRUE)]
colony.lms <- other.lms[setdiff(names(other.lms), names(temperature.lms))]
responsive.lms <- c(temperature.lms, interaction.lms)
rm(other.lms)
```

@@

* HighOn - expression activated at high temperatures
* PositiveLinear - expression positive linear across thermal gradient (0 - 38°C)
* LowOn - expression activated at low temperatures
* NegativeLinear - expression negative linear across thermal gradient (0 - 38°C)
* Intermediate - maximum expression at intermediate temperatures (14 - 28C)
* Bimodal - expressed greater than one standard deviation of expression at both low and high temperatures

@@

# Reorganize for plotting to show overlap among categories between colonies
type.table <- table(Ap.response.type[ , 'Ar.type'], Ap.response.type[ , 'A22.type'])
# reorder 
tt2 <- type.table[c("Bimodal", "PositiveLinear", "HighOn", "Intermediate", "NegativeLinear", "LowOn", "NotResp"), c("Bimodal", "PositiveLinear", "HighOn", "Intermediate", "NegativeLinear", "LowOn", "NotResp")]

@@

```{r temperature_response_table, echo=FALSE, results='asis'}
# add row and column totals
tt3 <- rbind(tt2, colSums(tt2))
tt3 <- cbind(tt3, rowSums(tt3))
colnames(tt3)[8] <- "Total"
rownames(tt3)[8] <- "Total"
# move names into table
tt3 <- rbind(rownames(tt3), tt3)
tt3 <- cbind(rownames(tt3), tt3)
# name col/row by species
rownames(tt3) <- c("AcNC", "", "", "", "", "", "", "", "")
colnames(tt3) <- c("ApVT", "", "", "", "", "", "", "", "")

@@

```{r optimum_expression_comparison}
# list of transcripts that are 'high' expressed in A22
A22.high.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "HighOn" | Ap.response.type$A22.type == "PositiveLinear"), ]

@@

```{r Ar_low_wilcoxon}
# list of transcripts that are 'high' expressed in Ar
Ar.low.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "LowOn" | Ap.response.type$A22.type == "NegativeLinear"), ]

@@

```{r extract_Transcripts}
A22.high.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "HighOn"), "Transcript"]
Ar.high.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "HighOn"), "Transcript"]

A22.poslinear.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "PositiveLinear"), "Transcript"]
Ar.poslinear.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "POsitiveLinear"), "Transcript"]

A22.low.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "LowOn"), "Transcript"]
Ar.low.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "LowOn"), "Transcript"]

A22.neglinear.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "NegativeLinear"), "Transcript"]
Ar.neglinear.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "NegativeLinear"), "Transcript"]

>>>>

# Load Bioconductor libraries
#source("http://bioconductor.org/biocLite.R")
#biocLite("topGO")
#biocLite("Rgraphviz")
#biocLite("RDAVIDWebService")
#biocLite("GOSemSim")
library(topGO) 
library(Rgraphviz)

library(GOSemSim)

@@

```{r responsive_transcripts}
grepFunc <- function(lmitem, term = NA) {
  coefs <- coefficients(lmitem)
  coef.names <- names(coefs)
  keep <- if(length(grep(term, coef.names)) > 0) TRUE else FALSE
}

interaction.lms <- RxNlmAIC[which(Map(grepFunc, RxNlmAIC, term = "colonyAr:") == TRUE)]
other.lms <- RxNlmAIC[setdiff(names(RxNlmAIC), names(interaction.lms))]
temperature.lms <- other.lms[which(Map(grepFunc, other.lms, term = "val") == TRUE)]
colony.lms <- other.lms[setdiff(names(other.lms), names(temperature.lms))]
responsive.lms <- c(temperature.lms, interaction.lms)
rm(other.lms)
```

@@

* High - increase expression with temperature
* Low - decrease expression with temperature
* Intermediate - maximum expression at intermediate temperatures (14 - 28C)
* Bimodal - expressed greater than one standard deviation of expression at both low and high temperatures

@@

# Reorganize for plotting to show overlap among categories between colonies
type.table <- table(Ap.response.type[ , 'Ar.type'], Ap.response.type[ , 'A22.type'])
# reorder 
tt2 <- type.table[c(2,4,1,3,5), c(2,4,1,3,5)]

@@

```{r temperature_response_table, echo=FALSE, results='asis'}
# add row and column totals
tt3 <- rbind(tt2, colSums(tt2))
tt3 <- cbind(tt3, rowSums(tt3))
colnames(tt3)[6] <- "Total"
rownames(tt3)[6] <- "Total"
# move names into table
tt3 <- rbind(rownames(tt3), tt3)
tt3 <- cbind(rownames(tt3), tt3)
# name col/row by species
rownames(tt3) <- c("AcNC", "", "", "", "", "", "")
colnames(tt3) <- c("ApVT", "", "", "", "", "", "")

@@

```{r optimum_expression_comparison}
# list of transcripts that are 'high' expressed in A22
A22.high.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "High"), ]

@@

```{r Ar_low_wilcoxon}
# list of transcripts that are 'high' expressed in Ar
Ar.low.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "Low"), ]

@@

```{r extract_Transcripts}
A22.high.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "High"), "Transcript"]
Ar.high.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "High"), "Transcript"]

A22.low.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "Low"), "Transcript"]
Ar.low.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "Low"), "Transcript"]
